Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-15 paper.qmd
Updated Figure 2 title

```{r}
#| label: fig-two-curvy-true-proj
#| fig-cap: "Two views of the true model (blue lines) in $2\\text{-}D$ projections from $7\\text{-}D$, for the two C-shaped clusters data (grey points). In one C-shaped cluster, the data is spread throughout the cluster, while in the other C-shaped cluster, the data is concentrated more in one corner of the cluster. The **langevitour** software is used to view the data with a tour, and the full video is available at <>." 
#| fig-pos: H
#| fig-width: 10
#| fig-height: 5

>>>>

```{r}
#| label: fig-two-curvy-true-proj
#| fig-cap: "Two projections from $7\\text{-}D$, for the two non-linear cluster data are shown. The sample obtained from the true model is shown, with the sample shown in grey and the true model in blue lines. In the C-shaped cluster, the data points are distributed randomly along the cluster, while the data is more concentrated more in one corner in the other non-linear cluster. Video of the langevitour animations are available at <>." 
#| fig-pos: H
#| fig-width: 10
#| fig-height: 5
